Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-16 05_calibration_data.Rmd
show data head

```{r}
# for data handling
library(data.table)
library(atlastools)

@@

```{r}
# read and plot example data
data <- fread("data/atlas1060_allTrials_annotated.csv")
data_raw <- copy(data)

>>>>

```{r eval=TRUE}
# for data handling
library(data.table)
library(atlastools)

@@

```{r, eval=TRUE}
# read and plot example data
data <- fread("data/atlas1060_allTrials_annotated.csv")
data_raw <- copy(data)
